---
title: "AI-Powered Employee Attrition Prediction System"
subtitle: "Executive Summary Report"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
params:
  raw_data: NA
  validation: NA
  trained_models: NA
  bulk_results: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
raw_data <- params$raw_data
validation <- params$validation
trained_models <- params$trained_models
bulk_results <- params$bulk_results
```

## 1. Dataset Summary

```{r}
if (!is.null(raw_data)) {
  cat("Total Employees:", nrow(raw_data), "\n")
  cat("Total Features:", ncol(raw_data), "\n")
  if ("Attrition" %in% names(raw_data)) {
    cat("Attrition Rate:", round(mean(raw_data$Attrition == "Yes", na.rm = TRUE) * 100, 1), "%\n")
  }
}
if (!is.null(validation)) {
  cat("Dataset Quality Score:", validation$quality_score, "/100\n")
}
```

## 2. Model Performance

```{r}
if (!is.null(trained_models) && length(trained_models) > 0) {
  tbl <- do.call(rbind, lapply(names(trained_models), function(nm) {
    m <- trained_models[[nm]]$metrics
    data.frame(Model = nm, Accuracy = round(m$Accuracy, 3), Precision = round(m$Precision, 3),
               Recall = round(m$Recall, 3), F1 = round(m$F1, 3), AUC = round(m$AUC, 3))
  }))
  knitr::kable(tbl)
} else {
  cat("No models trained yet.")
}
```

## 3. Risk Predictions Summary

```{r}
if (!is.null(bulk_results)) {
  cat("High Risk:", sum(bulk_results$RiskLabel == "High Risk"), "\n")
  cat("Moderate Risk:", sum(bulk_results$RiskLabel == "Moderate Risk"), "\n")
  cat("Low Risk:", sum(bulk_results$RiskLabel == "Low Risk"), "\n")
} else {
  cat("No bulk predictions run yet.")
}
```

## 4. Recommendations

Based on the risk analysis, HR teams should focus on:

- Reducing mandatory overtime in high-risk departments
- Reviewing compensation for employees below market salary bands
- Strengthening onboarding and mentorship for employees in their first two years
- Running regular employee engagement and satisfaction surveys

---
*Generated automatically by the AI-Powered Employee Attrition Prediction System.*
